Decision Trees for SP500 feature set
======================================
Robert Sloan    
June 20, 2014    
This is a work in progress... 
TODO
[ ]  Still figuring out how to plot
    
Investigating creating Decision trees   
This is a R Markdown file    
Load into R Studio.  install.packages("knitr") if not already done so    
Run by clickin on the 'Knit HTML' icon in the title bar above code view    
    
load and display start of feature file   

```{r load feature file}
# The 'rpart' package provides the 'rpart' function.
require(rpart, quietly=TRUE)

setwd("/Users/Robert/Dropbox/Class/Mr Stock Market meet Mr Data Scientist/data")
#read in Feature file
sp500f <- read.table(file = "featuresSP500.csv", header=TRUE, sep=",")
#remove columns 'Date' and 'CLose'
sp500f <- sp500f[,-which(names(sp500f) %in% c("Date","Close"))]

head(sp500f)  
```    
    
Create Decision Tree    
    
```{r simple linear model}
#fit<-lm(leadcp~lag_cp1d+lag_cp2d+lag_cp1w+ma100+Volume,data=sp500f)
tree <- rpart(lead_1d ~ .,
                   data=sp500f,
                   method="anova")
```   
    
Print tree results    
      
```{r print tree text results}
print(tree)
printcp(tree)
cat("\n")
```
    
Plot the Decision Treee    
    
```{r Plot the Decision Tree}
# Plot the resulting Decision Tree.
# usint the rpart.plot package.
plot(tree, main="Decision Tree Features")
```

