Exploring SP500 Feature set
======================================
Robert Sloan    
June 12, 2014
This is a work in progress...     
    
Exploring feature file     
This is a R Markdown file    
Load into R Studio.  install.packages("knitr") if not already done so    
Run by clickin on the 'Knit HTML' icon in the title bar above code view    
    
load and display start of feature file    
Change working directory to where feature file is stored    
```{r load feature file, cache=TRUE}
setwd("/Users/Robert/Dropbox/Class/Mr Stock Market meet Mr Data Scientist/data")
#read in Feature file
sp500f <- read.table(file = "featuresSP500.csv", header=TRUE, sep=",")
head(sp500f)   
```
    
Investigating the correlation between features
```{r Pairwise feature comparison, cache=TRUE}
pairs(leadcp~lag_cp1d+lag_cp2d+ma100+Volume, data=sp500f)  # 
```
    
Summarize data
```{r data summary}
summary(sp500f)
```
    
Structure of data
```{r data structure}
str(sp500f)
```
    
Look for missing data
```{r missing data}
# diminsions
dim(sp500f)

# checking for missing data
a <- na.omit(sp500f)
dim(a)  # if dimension are the same no missing data
```
    
Histograms
```{r histograms}
hist(sp500f$lag_cp1d,main="1 day lag",breaks=100)
hist(sp500f$lag_cp2d,main="2 day lag",breaks=100)
hist(sp500f$ma100,main="100 Day Moving Average",breaks=100)
hist(sp500f$Volume,main="Volume",breaks=100,ylim=c(0,2000))
```
