Exploring SP500 Feature set
======================================
Robert Sloan    
June 12, 2014
This is a work in progress...     
TODO    
[ ] Add more tests for correlations between features and target       

    
Exploring feature file     
This is a R Markdown file    
Load into R Studio.  install.packages("knitr") if not already done so    
Run by clickin on the 'Knit HTML' icon in the title bar above code view    
    
load and display start of feature file    
Change working directory to where feature file is stored  

```{r load feature file, cache=TRUE}
setwd("/Users/Robert/Dropbox/Class/Mr Stock Market meet Mr Data Scientist/data")
#read in Feature file
sp500f <- read.table(file = "featuresSP500.csv", header=TRUE, sep=",")
#remove columns 'Date' and 'CLose'
sp500f <- sp500f[,-which(names(sp500f) %in% c("Date","Close"))]
head(sp500f)   
```
    
    
Summarize data
```{r data summary}
summary(sp500f)
```
    
Structure of data
```{r data structure}
str(sp500f)
```
    
Look for missing data
```{r missing data}
# diminsions
dim(sp500f)

# checking for missing data
a <- na.omit(sp500f)
dim(a)  # if dimension are the same no missing data
```
     
 Dependence Tests    
      
```{r dependance tests, cache=TRUE} 
# There should be a way to do this automatically for all features 
mytable <- xtabs(~lead_1d+lag_1d, data=sp500f)
chisq.test(mytable)
library(vcd)
assocstats(mytable) 
``` 
 
Histograms
```{r histograms}

for (i in 1:(length(sp500f)-1)) {
#    hist(sp500f[,i],main=colnames(sp500f)[i],breaks=100)
    hist(sp500f[,i],breaks=100)
}


#hist(sp500f$lag_cp1d,main="1 day lag",breaks=100)
#hist(sp500f$lag_cp2d,main="2 day lag",breaks=100)
#hist(sp500f$ma100,main="100 Day Moving Average",breaks=100)
#hist(sp500f$Volume,main="Volume",breaks=100,ylim=c(0,2000))
```


Investigating the correlation between features 
NOTE:  with many features this takes a very long time
    
```{r Pairwise feature comparison, cache=TRUE}
pairs(lead_1d ~ ., data=sp500f)  # 
```
