Linear Prediction for SP500 feature set
======================================
Robert Sloan    
June 12, 2014    
This is a work in progress...    
    
Investigating fitting Linear model    
This is a R Markdown file    
Load into R Studio.  install.packages("knitr") if not already done so    
Run by clickin on the 'Knit HTML' icon in the title bar above code view    
    
load and display start of feature file   
    
```{r load feature file}
setwd("/Users/Robert/Dropbox/Class/Mr Stock Market meet Mr Data Scientist/data")
#read in Feature file
sp500f <- read.table(file = "featuresSP500.csv", header=TRUE, sep=",")
head(sp500f)   
```
    
Fit Linear Model    
    
```{r simple linear model}
fit<-lm(leadcp~lag_cp1d+lag_cp2d+lag_cp1w+ma100+Volume,data=sp500f)
```   
           
summary and anova    

```{r summary and anova}
anova(fit)  # correctness of model
summary(fit) #summary of model
```
    
Summary table of regression coefficients    
    
```{r summary table, results='asis'}
library(xtable)
xt<-xtable(summary(fit))
print(xt,type="html")
```


Analysis of variance table    
    
```{r anova table, results='asis'}
xt<-xtable(anova(fit)) # correctness of model
print(xt,type="html") 
```    
 
   
Plot of residuals etc    
    
```{r residual plots}
opar <- par(mfrow = c(2,2), oma = c(0, 0, 1.1, 0))
plot(fit, las = 1)      # Residuals, Fitted, ...
par(opar)
```




